### 2015-12-30 fundamentals/examples.tex
adds image and eqns for LP formulation

To illustrate the flexibility of \Cyclus, this section will discuss the 
creation and results of a range of representative fuel cycle simulations.
Previous benchmarks between 
\Cyclus and system dynamics simulators for more complex problems, including 
transition analyses, have been reported 
elsewhere and \Cyclus has demonstrated satisfactory performance
\cite{djokic_application_2015,scopatz_non-judgemental_2015,gidden_once-through_2012} . 
The current examples are not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus matches the capabilities of any
recipe-based simulator and that variations on a single \Cyclus simulations can 
be run with small changes to the input specification. 
For simplicity of the current demonstration, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:

>>>>

To illustrate the flexibility of \Cyclus, this section will discuss the 
creation and results of a range of representative fuel cycle simulations.
Previous benchmarks between 
\Cyclus and system dynamics simulators for more complex problems, including 
transition analyses, have been reported 
elsewhere and \Cyclus has demonstrated satisfactory performance
\cite{djokic_application_2015,scopatz_non-judgemental_2015,gidden_agent-based_2015,gidden_once-through_2012} . 
The examples presented here are not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus matches the capabilities of any
recipe-based simulator and that variations on a single \Cyclus simulations can 
be run with small changes to the input specification. 
For simplicity of the current demonstration, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:

### 2015-12-30 fundamentals/impl.tex
adds image and eqns for LP formulation

Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle \Cyclus-enabled 
application on such a large compute system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to study \gls{DRE} performance and
outcomes. For example, an investigation of the effect of solution degeneracy, a
commonly observed phenomenon in scenarios with individual facilities and basic
(e.g., commodity-only) preference definitions, was performed for three different
fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
coefficients were generated based on two factors: commodity-facility pairings
and facility location. The population of the possible values of
commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
population of possible values of the location effect was investigated for values
of zero, ten, and infinity (i.e., any real number). The study additionally
included an investigation of problem-scaling behavior in order to quantify the
magnitude and rate-of-increase of DRE solution times as a function of the
simulation-entity population for each fuel
cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
has separately been utilized to run and collect information from full \Cyclus
simulations running in parallel on $10^3$ machines reliably for order $10^5$
simulations.

@@

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2015}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, \glspl{LP} solve much faster than
\glspl{MILP}. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.

>>>>

Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle \Cyclus-enabled 
application on such a large compute system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to study \gls{DRE} performance and
outcomes. For example, an investigation of the effect of solution degeneracy, a
commonly observed phenomenon in scenarios with individual facilities and basic
(e.g., commodity-only) preference definitions, was performed for three different
fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
coefficients were generated based on two factors: commodity-facility pairings
and facility location. The population of the possible values of
commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
population of possible values of the location effect was investigated for values
of zero, ten, and infinity (i.e., any real number). The study additionally
included an investigation of problem-scaling behavior in order to quantify the
magnitude and rate-of-increase of \gls{DRE} solution times as a function of the
simulation-entity population for each fuel
cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
has separately been utilized to run and collect information from full \Cyclus
simulations running in parallel on $10^3$ machines reliably for order $10^5$
simulations.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\columnwidth]{./images/bid_req}
\end{center}
\caption{The flow graph representing three suppliers (left), two requesters (right), 
and the potential flows of various commodities among them. 
The second consumer makes two different requests.
Meanwhile, the second supplier can supply the commodities 
requested by both consumers and has provided two bids accordingly 
\cite{gidden_agent-based_2015}.}
\label{fig:bid_req}
\end{figure}

Given a full definition of supply and demand, represented in Figure 
\ref{fig:bid_req} as a flow graph, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2015}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. The \gls{LP} formulation in \Cyclus is of the 
form given by Gidden \cite{gidden_agent-based_2015}:

\begin{align}
\min_{x} z &= \sum_{i\in I}\sum_{j\in J} c_{i,j}x_{i,j}& &\\
s.t & \sum_{i\in I_s}\sum_{j\in J} a_{i,j}^k x_{i,j} \le b_s^k & & \forall k\in K_s, \forall s\in S\\
    & \sum_{J\in J_r}\sum_{i\in I} a_{i,j}^k x_{i,j} \le b_r^k & & \forall k\in K_r, \forall r\in R\\
    & x_{i,j} \in [0,x_j] & & \forall i\in I, \forall j\in J
\end{align}
\begin{align}
\intertext{where}
S &= \mbox{suppliers}\nonumber\\
R &= \mbox{requesters}\nonumber\\
I_s &= \mbox{supply nodes for a supplier s}\nonumber\\
J_r &= \mbox{all request nodes for a requester r}\nonumber\\
K_s &= \mbox{constraints for a supplier s}\nonumber\\
K_r &= \mbox{constraints for a requester r}\nonumber\\
X &= \mbox{potential commodity flows}\nonumber\\
c_{i,j} &= \mbox{unit cost of flow from i to j}\nonumber\\
x_{i,j} &= \mbox{flow from node i to node j}\nonumber\\
a^k_{i,j} &= \mbox{constraint coeffiecient between i and j}\nonumber\\
b^k_s  &= \mbox{constraint k of supplier s}\nonumber\\
b^k_r &= \mbox{constraint k of requester r}\nonumber\\
\tilde{x}_j &= \mbox{requested quantity of request node j.}\nonumber
\end{align}

In practice, \glspl{LP} solve much faster than
\glspl{MILP}. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.
